\documentclass[]{article}
\usepackage{lmodern}
\usepackage{amssymb,amsmath}
\usepackage{ifxetex,ifluatex}
\usepackage{fixltx2e} % provides \textsubscript
\ifnum 0\ifxetex 1\fi\ifluatex 1\fi=0 % if pdftex
  \usepackage[T1]{fontenc}
  \usepackage[utf8]{inputenc}
\else % if luatex or xelatex
  \ifxetex
    \usepackage{mathspec}
  \else
    \usepackage{fontspec}
  \fi
  \defaultfontfeatures{Ligatures=TeX,Scale=MatchLowercase}
\fi
% use upquote if available, for straight quotes in verbatim environments
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
% use microtype if available
\IfFileExists{microtype.sty}{%
\usepackage[]{microtype}
\UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
}{}
\PassOptionsToPackage{hyphens}{url} % url is loaded by hyperref
\usepackage[unicode=true]{hyperref}
\hypersetup{
            pdfborder={0 0 0},
            breaklinks=true}
\urlstyle{same}  % don't use monospace font for urls
\usepackage[margin=1in]{geometry}
\IfFileExists{parskip.sty}{%
\usepackage{parskip}
}{% else
\setlength{\parindent}{0pt}
\setlength{\parskip}{6pt plus 2pt minus 1pt}
}
\setlength{\emergencystretch}{3em}  % prevent overfull lines
\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}
\setcounter{secnumdepth}{0}
% Redefines (sub)paragraphs to behave more like sections
\ifx\paragraph\undefined\else
\let\oldparagraph\paragraph
\renewcommand{\paragraph}[1]{\oldparagraph{#1}\mbox{}}
\fi
\ifx\subparagraph\undefined\else
\let\oldsubparagraph\subparagraph
\renewcommand{\subparagraph}[1]{\oldsubparagraph{#1}\mbox{}}
\fi

% set default figure placement to htbp
\makeatletter
\def\fps@figure{htbp}
\makeatother


\date{}

\begin{document}

\section{Benjamin Connelly}\label{benjamin-connelly}

415-917-0763\\
New Orleans, LA 70115\\
benjamin.t.connelly@gmail.com\\
http://www.linkedin.com/in/benjaminconnelly

\section{Summary}\label{summary}

Operations Engineer with a strong background in Linux deployments,
automation, monitoring / metrics, configuration management,
troubleshooting and maintenance.

\section{Work Experience}\label{work-experience}

\subsection{iSeatz (New Orleans, LA)}\label{iseatz-new-orleans-la}

\textbf{Cloud Operations Engineer} (May 2016 - Present)

\begin{itemize}
\tightlist
\item
  Remote administration of multiple Production, Staging, and QA
  environments hosted at AWS.
\item
  Provisioning and Configuration Management with Salt Stack.
\item
  Proactive monitoring and alerting of all systems and micro-services
  with Datadog, Sumo, and PagerDuty.
\item
  Automation of manual tasks for all departments with BASH, Python, and
  PhantomJS/CasperJS.
\item
  Managing and reporting on cost of AWS infrastructure with CloudHealth.
\item
  Management of AWS Reserved Instance pools. \textbf{+\$250,000 savings
  this year}
\item
  Orchestration of vendor selection, contract negotiation and/or renewal
  processes, ongoing cost management, deployment, and administration of
  all third party vendors.
\end{itemize}

\subsection{The Zoo Studios (Oakland,
California)}\label{the-zoo-studios-oakland-california}

\textbf{Systems Administrator} (May 2012 - November 2016)

\begin{itemize}
\tightlist
\item
  Disaster recovery, deployment, and configuration management for over
  100 Amazon AWS accounts based on Vagrant and Ansible.
\item
  Developed automated deployment and self healing monitoring of the
  building's Linux servers used for key entry system, security alarms,
  environment controls, lighting controls, and phone system based on
  Bash scripts and Ansible.
\item
  OS X server and workstation administration in a variety of
  configurations for recording artists, mixing engineers, and business
  personal.
\end{itemize}

\subsection{Ebay / StubHub (San Francisco,
California)}\label{ebay-stubhub-san-francisco-california}

\textbf{Senior Linux Systems Administrator} (2004 - 2012)

\begin{itemize}
\tightlist
\item
  Design, deployment, and administration of production environment for
  www.stubhub.com.
\item
  Design, deployment, and administration of 30+ development environments
  across multiple data centers.
\item
  Manage F5 BigIP load balancers for development environments.
\item
  Configuration of Apache, Jboss, JMS, ColdfusionMX, ActiveMQ, Solr,
  Bind, Sendmail, and Oracle g.
\item
  24/7 on call for production environment, www.stubhub.com.
\item
  Monitor, respond to, and administer network equipment, traffic, and
  connections in the core network.
\end{itemize}

\end{document}
